{\datastorr}: A package for distributing dynamic and versioned data

### 2017-04-24 ms.tex
some work on tables

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{Biomass And Allometry Database} \citep{Falster-2015}
\item
  \texttt{taxonlookup} \citep{Pennell-2015a}
\item
  \texttt{plantgrowthform}
\end{enumerate}

@@

\begin{table}[h!]
\centering
\caption{Alternative frameworks for managing a living database}
{\footnotesize
\vspace{1cm}
  \begin{tabular}{p{5cm}p{5cm}p{5cm}}
  \hline
  \textbf{Feature} & \textbf{Traditional web database} & \textbf{Lightweight versioned data}\\ \hline
   Data storage     & SQL           &  git       \\
   Webserver        & custom        &  Maintained by github.com\\
   Frontend         & Ruby on rails &  datastorr \\
   Ease of setup    & Easy          & Moderate \\ % server, backups, bandwidth
   Data size        & Small-Very large & Up to 1Gb\\
   Cost             & Ongoing       & Free \\
   Bandwidth        & Pro rata      & Managed by github.com\\
   Maintainer skills& Ruby, php     & R, git \\
   User skills      & Web           & R \\
   Versioning       & Hard          & Easy \\
   DOI minting      & Manual        & Automatic \\
  \hline
  \end{tabular}
  }
\label{tab:sql_v_versioneddata}
\end{table}

@@

\begin{table}[h!]
\centering
\caption{Main technologies leveraged to store and distribute "Lightweight versioned data".}
{\footnotesize
\vspace{1cm}
  \begin{tabular}{p{5cm}p{10cm}}
  \hline
  \textbf{Technology} & \textbf{Description} \\\hline
   git & Open source version control system used for tracking progressive changes in a set of text files, typically computer code but also data\\
   github.com & A commercial webplatform for sharing, visualising and managing `git' repositories. Includes issue tracking.\\
   R     &  Open source statsitcial and data processing language. \\
   CRAN  &  Open source repository of packages for the R language \\
   datastorr & R package used to fetch github releases. \\
   \hline
  \end{tabular}
  }
\label{tab:technologies}
\end{table}

@@

\begin{table}[h!]
\centering
\caption{Groups of users and their requirements}
{\footnotesize
\vspace{1cm}
  \begin{tabular}{p{2cm}p{5cm}p{7cm}}
  \hline
  \textbf{Group} & \textbf{Goal} & \textbf{Requirements} \\ \hline
  Maintainer & Create and distribute versioned datasets & Low technical overhead \\
    & & Easy workflow for releasing new versions \\
    & & Long term preservation \\
    & & Easy to crowd-source contributions \\
    & & Low cost \\
    & & Low maintenance \\
  Contributor & Contribute to future versions & Add new data \\
    & & Report errors in existing data  \\
  Users (all) & Easy access to releases & Introduction \& overview \\
    & & Long term stability \\
    & & Clear path for user to become contributor \\
  Users (computational, machines) & Scripted access to releases & Easy installation\\
    & & Long term stability \\
  \hline
  \end{tabular}
  }
\label{tab:user_requirements}
\end{table}

>>>>

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{coraltraits}
\item
  \texttt{Biomass And Allometry Database} \citep{Falster-2015}
\item
  \texttt{taxonlookup} \citep{Pennell-2015a}
\item
  \texttt{plantgrowthform}
\end{enumerate}

@@

\begin{table}[h!]
\centering
\caption{Alternative frameworks for setting up and managing a living database}
{\footnotesize
\vspace{1cm}
  \begin{tabular}{p{2.5cm}p{3.5cm}p{3.5cm}p{4cm}}
  \hline
  \textbf{Feature} & \textbf{Static data}& \textbf{Web database} & \textbf{Lightweight versioned data}\\ 
  \hline
   Webserver        & dataDryad or others & custom                          &  Maintained by github.com\\
   Backend          & none & SQL + Ruby-on-rails 			& git + datastorr \\
   User access      & Web browser & Web browser 				    & R \\
   Ease of setup    & Very easy & Moderate 							& Easy\\ % server, backups, bandwidth
   Data size        &Up to several Gb & Small-Very large 				& Up to 1Gb\\
   Cost             &Varies & Varies  						& Free \\
   Bandwidth        &managed by dataDryad & Pro rata 						& Managed by github.com\\
   Maintainer skills &none & Ruby + php 					& R + git \\
   User skills      &Web browsing& Web browsing  					& basic R \\
   Versioning       &None& Hard 							& Easy \\
   DOI minting      &Automatic & Many steps 					& Automatic \\
  \hline 
  \\

  \end{tabular}
  } 
\label{tab:sql_v_versioneddata}
\end{table}

@@

\begin{table}[h!]
\centering
\caption{Main technologies leveraged to store and distribute "Lightweight versioned data".}
{\footnotesize
\vspace{1cm}
  \begin{tabular}{p{5cm}p{10cm}}
  \hline
  \textbf{Technology} & \textbf{Description} \\\hline
   git & Open source version control system used for tracking progressive changes in a set of text files, typically computer code but also data\\
   github.com & A commercial webplatform for sharing, visualising and managing `git' repositories. Includes issue tracking.\\
   R     &  Open source statsitcial and data processing language. \\
   CRAN  &  Open source repository of packages for the R language \\
   datastorr & R package used to fetch github releases. \\
   DOI & Digital object identifier, which refers a user to a single stable digital object \\ 
   DOI ``minting'' & creation of DOI's \\
   \hline
  \end{tabular}
  }
\label{tab:technologies}
\end{table}

@@

\begin{table}[h!]
\centering
\caption{Groups of users and their requirements}
{\footnotesize
\vspace{1cm}
  \begin{tabular}{p{2cm}p{5cm}p{7cm}}
  \hline
  \textbf{Group} & \textbf{Goal} & \textbf{Requirements} \\ \hline
  Maintainer & Create and distribute versioned datasets & Low technical overhead \\
    & & Easy workflow for releasing new versions \\
    & & Long term preservation \\
    & & Easy to crowd-source error checking and contributions \\
    & & Low initial cost \\
    & & Low on-going maintenance \\
  Contributor & Contribute to future versions & Add new data \\
    & & Report errors in existing data  \\
  Users (all) & Easy access to releases & Introduction \& overview \\
    & & Long term stability \\
    & & Clear path for users to become contributors \\
  Users (computational, machines) & Build reproducible products on these data & Scripted access to releases\\
    & &Easy installation\\
    & & Long term stability \\
  \hline
  \end{tabular}
  }
\label{tab:user_requirements}
\end{table}
